Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-29 W13report.tex
Consistency on visit names

A set of ``heat maps'' is presented in Figure~\ref{fp_heatmap}, that
demonstrate the total number of detections across all 9 sensors as a
function of the config parameters spatialKernelOrder and degGauss, for
nGauss = 3.  Qualitatively, these heat maps indicate that a Chebyshev
spatial order greater than 3 is required for all data.  In addition,
with the exception of the deconvolution case (visit 6866601 and
prefilter=False), the Gaussians need to be modified by Laguerre
polynomials of order 4 or higher.  The minimum of these detection maps
are found using the configs of highest complexity, with a very flat
slope in the number of false detections beyond spatialKernelOrder$>$3
and degGauss$>$3.  There is not much evidence for an upturn in the
numbers of false detections, meaning we have likely not reached the
case of severe overfitting using these configs.

@@

Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
Using a Monte Carlo approach we 
estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
detections come primarily from detection of the ringing around stars.

In all cases the empirical results are below the predicted results indicating
that the number counts are smaller than the theoretical floor.  {\bf What should we say about this here?} We can correct for this by scaling
the prediction by 2.5\%, 1.5\% and 1\% for visits 6866601, 6866602, and 6866603 respectively.  The data plotted with these corrections are shown
in the bottom row.  Once this correction is done, the trend of false positive rate with detection threshold agrees to within 1-$\sigma$ for the 
prefiltering case for all three seeing values.

>>>>

A set of ``heat maps'' is presented in Figure~\ref{fp_heatmap}, that
demonstrate the total number of detections across all 9 sensors as a
function of the config parameters spatialKernelOrder and degGauss, for
nGauss = 3.  Qualitatively, these heat maps indicate that a Chebyshev
spatial order greater than 3 is required for all data.  In addition,
with the exception of the deconvolution case (v6866601 and
prefilter=False), the Gaussians need to be modified by Laguerre
polynomials of order 4 or higher.  The minimum of these detection maps
are found using the configs of highest complexity, with a very flat
slope in the number of false detections beyond spatialKernelOrder$>$3
and degGauss$>$3.  There is not much evidence for an upturn in the
numbers of false detections, meaning we have likely not reached the
case of severe overfitting using these configs.

@@

Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
Using a Monte Carlo approach we 
estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
as shaded grey about the model line in dark black.  From left to right the panels are for v6866601 -- 0.6$^{\prime\prime}$ FWHM,
v6866602 -- 0.88$^{\prime\prime}$ FWHM and v6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
in the postfiltering case (v6866601) the count rates between the two algorithms agree very well when corrected for the
observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
detections come primarily from detection of the ringing around stars.

In all cases the empirical results are below the predicted results indicating
that the number counts are smaller than the theoretical floor.  {\bf What should we say about this here?} We can correct for this by scaling
the prediction by 2.5\%, 1.5\% and 1\% for v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
in the bottom row.  Once this correction is done, the trend of false positive rate with detection threshold agrees to within 1-$\sigma$ for the 
prefiltering case for all three seeing values.
